---
title: "Gapminder Analysis"
author: "Indika Mallawaarachchi"
date: "10/14/2019"
output:
  html_document:
    keep_md: yes
    fig_caption: yes
    toc: yes
  pdf_document:
    toc: yes
---

# Introduction

Here is my first R Markdown document.

# Let's embed some R code

We'll write an R chunk that loads the tidyverse package and then reads in the Gapminder datset from the data of the project.

CTRL+ALT+i (to insert code chunk)

```{r}
library(tidyverse)
gm <- read.csv("Data/gapminder.csv")
```

# Investigate gm data

```{r}
head(gm)
```

# Our first plot

Showing life expentancy vs gdp per capita 

```{r, fig.cap="Fig1: Life expentancy vs GDP"}
ggplot(gm,aes(x=gdpPercap, y=lifeExp))+geom_point()
```


# Better plot

Showing life expentancy vs gdp per capita 

```{r, fig.cap="Fig1: Life expentancy vs GDP"}
ggplot(gm,aes(x=gdpPercap, y=lifeExp))+geom_point(aes(col=continent))+
  scale_x_log10()
```

# Possible chunk options

https://yihui.name/knitr/options/

Options include:
- echo (TRUE by default) whether to include code in output
- results 
  - hide will hide the results
  - hold will hold all the results until the end of r chuck (show the code first and results later)
  - include (TRUE by default) if FALSE then the code will not run
  - fig.width, fig.height set the figure dimentions in the output
  - cache (FALSE by default) if TRUE save results from R chunk for the next time to save running time. Just running the new code.

# Better plot changing dimetions

Showing life expentancy vs gdp per capita 

```{r, fig.cap="Fig1: Life expentancy vs GDP", fig.width=4}
ggplot(gm,aes(x=gdpPercap, y=lifeExp))+geom_point(aes(col=continent))+
  scale_x_log10()
```

# RMarkdown table

see some data using head function

```{r}
head(gm)
```

new head function as a table

```{r}
library(knitr)
kable(head(gm))
```

if you like tables, look at **gt** table package.

